\thesistitle

### 2019-07-25 sections/introduction.tex
Intro

\section{Contributions}
\todo{Rewrite this part}
Our research makes the following contributions:
\begin{enumerate}
	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
\end{enumerate}

>>>>

\section{Contributions}
\todo{TODO}
%Our research makes the following contributions:
%\begin{enumerate}
%	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
%	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
%	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
%	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
%\end{enumerate}
